---
title: "Emotion analysis results: Frankfurter Allgemeine Zeitung (F.A.Z.)"
author: "Felix Aubele"
date: "01-12-2022"
output:
  pdf_document: default
  html_document: default
  editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
# ==============================================================================
#                             DIW Berlin
#
# Project:  Wohnkosten, Lebenszufriedenheit, Sicherheitsempfinden und Narrative: 
#           Eine Betrachtung der langfristigen Verteilungswirkungen von
#           Wohnungsmarktzyklen (2020-2023)
#
# ------------------------------------------------------------------------------
#
#	 	CONTENT: RESULTS FROM EMOTION ANALYSIS (F.A.Z.)
#
# 	OUTLINE: PART 1: Load results from emotion analysis
#				     PART 2: Clean and recode data
#                 2.1 Rename topics and categories
#                 2.2 Aggregate emotion scores to main and sub topic level
#				     PART 3:List with top words per emotion
#				     PART 4: Plots
#                 4.1 Full sample
#                 4.2 By main topic
#                 4.3 By sub topic
#
# -------------------------------------------------------------------------------
# code author: Felix Aubele (DIW Berlin)
#
# First created --- November 8, 2022										
# Last modified --- December 01, 2022 (cs)
# ------------------------------------------------------------------------------
# content: Analyses the emotions in the housing market articles of the newspaper
# 'F.A.Z.'.
# ==============================================================================

# ==============================================================================
# 0) Initial settings
# ==============================================================================

# clean
# -----
rm(list = ls())


# load libraries
# --------------
library(openxlsx)
library(stringr) # To use function str_replace
library(XML)
library(tidyverse)
library(patchwork)
library(viridis)

# set R system language (including dates etc.) to German
# ------------------------------------------------------
Sys.setlocale('LC_ALL', 'german')


# define threshold of keywords for article selection
# --------------------------------------------------
cKeyword1 = 1  #old keyword list
cKeyword2 = 1   #new keyword list


# select keyword approach
# -----------------------
vKeyword1 = "new"

# choose emotions dictionary
# --------------------------
dict = "custom_nrc"

# with or without lemmatization
# -----------------------------
lemma = "with"

# define paths and data input/output names
# ----------------------------------------
sFolder1 = "" # path where data, drafts etc. are stored
sFolder2 = "" # path where data, drafts etc. are stored
sInFile1 = paste("Data/FAZ/articlelists_sentiment/emotion_analysis_FAZ_Housing_", dict,"_", lemma, "_lemma.xlsx", sep="")
sInFile2 = "Data/nrc/Housing_emotion_custom_dict.xlsx"
sInFile3 = "data-preparation/German_specific_letters.xlsx"
sInFile4 = paste("Data/FAZ/articlelists_sentiment/emotion_analysis_FAZ_Housing_substudy_", dict,"_", lemma, "_lemma.xlsx", sep="")
sInFile5 = paste0("Data/FAZ/articlelists_sentiment/FAZ_Housing_emotion_count ", dict, ".xlsx")
sInFile6 = paste0("Data/FAZ/articlelists_sentiment/FAZ_Housing_emotion_count.xlsx")

sOutFile = "Draft/figures/sentiment-analysis/emotion analysis/fig_emotion_analysis_FAZ.pdf"
```


Die mit den Emotionswörterbüchern bewerteten Artikel werden eingeladen.  Auch werden die Anzahl der Emotionswörter aus den jeweiligen Texten geladen.

```{r}
# ==============================================================================
# 1) Load results from emotion analysis
# ==============================================================================

# load data
#---------
Y = read.xlsx(paste(sFolder1, sInFile1, sep=""))

# number of emotion words in text
# -------------------------------
emotions_count_full = read.xlsx(paste(sFolder1, sInFile6, sep=""))

```

## Datenaufbereitung

```{r}

# ==============================================================================
# 2) Clean and recode data
# ==============================================================================

# ==============================================================================
# 2.1) Rename topics and categories
# ==============================================================================

# filter unique articles and replace NAs
# --------------------------------------
Y = unique(Y)
Y = replace(Y, is.na(Y), 0)


# recode 'Year' as numeric
# -------------------------
Y$Year <- as.integer(Y$Year)

table(Y$LDA_topic_1_name)


# recode main topics
# ------------------
Y = Y %>% mutate(LDA_topic_1_catnew = case_when(
  LDA_topic_1==2 |  LDA_topic_1==4 |  LDA_topic_1==7 ~ "Wirtschaft"
  ,LDA_topic_1==5  |  LDA_topic_1==9 |LDA_topic_1==3 ~ "Politik"
  ,LDA_topic_1==6 |  LDA_topic_1==10  ~ "Andere Politikfelder"
  ,LDA_topic_1==1 |  LDA_topic_1==8 ~ "Wohnraum als Lebensraum"))
table(Y$LDA_topic_1_catnew,useNA="ifany")

# recode sub topics
# ------------------
Y = Y %>% mutate(LDA_topic_1_name_new = case_when(
  LDA_topic_1==1 ~ "Architektur und \n Stadtbild"
  , LDA_topic_1==2 ~ "Miet- und \n Baupreisentwicklung"
  , LDA_topic_1==3 ~ "Wohnsituation \n und -politik \n (Rhein-Main)"
  , LDA_topic_1==4 ~ "Immobilienmarkt"
  , LDA_topic_1==5 ~ "Wohnungspolitik \n im Wahlkampf \n (Rhein-Main)"
  , LDA_topic_1==6 ~ "Weltpolitik"
  , LDA_topic_1==7 ~ "Wohnungsbau \n (Rhein-Main)"
  , LDA_topic_1==8 ~ "Familienleben und \n Wohnumfeld"
  , LDA_topic_1==9 ~ "Wohnungspolitik auf \n Bundesebene"
  , LDA_topic_1==10 ~ "Unternehmen und Arbeitswelt"))
table(Y$LDA_topic_1_name_new,useNA="ifany")


# Delete all articles with category 'Andere Politikfelder'
# --------------------------------------------------------
Y_relev = Y %>% filter(LDA_topic_1_catnew!= "Andere Politikfelder")

# rename columns
# --------------
Y_relev = Y_relev %>% rename(Thema = LDA_topic_1_name_new
                             , Kategorie = LDA_topic_1_catnew)

#create list with German emotion names
# -------------------------------------
emotions <- c("Wut", "Erwartung", "Ekel",
              "Angst", "Freude", "Traurigkeit", "Überraschung", "Vertrauen")


# ==============================================================================
# 2.2) Aggregate emotion scores to main and sub topic level
# ==============================================================================

# full sample: calculate average emotion score per year
# ---------------------------------------------------------
Y_aggr <- as_tibble(Y)%>%
  mutate(
    Anger_weight = (Anger_weight/n_words)*100,
    Anticipation_weight = (Anticipation_weight/n_words)*100,
    Disgust_weight = (Disgust_weight/n_words)*100,
    Fear_weight = (Fear_weight/n_words)*100,
    Joy_weight = (Joy_weight/n_words)*100,
    Sadness_weight = (Sadness_weight/n_words)*100,
    Surprise_weight = (Surprise_weight/n_words)*100,
    Trust_weight = (Trust_weight/n_words)*100
  )%>%
  group_by(Year)%>%
  summarise(
    Anger_mean = mean(Anger_weight),
    Anticipation_mean = mean(Anticipation_weight),
    Disgust_mean = mean(Disgust_weight),
    Fear_mean = mean(Fear_weight),
    Joy_mean = mean(Joy_weight),
    Sadness_mean = mean(Sadness_weight),
    Surprise_mean = mean(Surprise_weight),
    Trust_mean = mean(Trust_weight)
  )



# main topic: calculate average emotion score per year and main topic
# ----------------------------------------------------------------------
Y_aggr_categ <- as_tibble(Y_relev)%>%
   mutate(
    Anger_weight = (Anger_weight/n_words)*100,
    Anticipation_weight = (Anticipation_weight/n_words)*100,
    Disgust_weight = (Disgust_weight/n_words)*100,
    Fear_weight = (Fear_weight/n_words)*100,
    Joy_weight = (Joy_weight/n_words)*100,
    Sadness_weight = (Sadness_weight/n_words)*100,
    Surprise_weight = (Surprise_weight/n_words)*100,
    Trust_weight = (Trust_weight/n_words)*100
  )%>%
  group_by(Year, Kategorie)%>%
  summarise(
    Anger_mean = mean(Anger_weight),
    Anticipation_mean = mean(Anticipation_weight),
    Disgust_mean = mean(Disgust_weight),
    Fear_mean = mean(Fear_weight),
    Joy_mean = mean(Joy_weight),
    Sadness_mean = mean(Sadness_weight),
    Surprise_mean = mean(Surprise_weight),
    Trust_mean = mean(Trust_weight)
  )

# sub topics: calculate average emotion score per year and sub topic
# ----------------------------------------------------------------------
Y_aggr_lda <- as_tibble(Y_relev)%>%
   mutate(
    Anger_weight = (Anger_weight/n_words)*100,
    Anticipation_weight = (Anticipation_weight/n_words)*100,
    Disgust_weight = (Disgust_weight/n_words)*100,
    Fear_weight = (Fear_weight/n_words)*100,
    Joy_weight = (Joy_weight/n_words)*100,
    Sadness_weight = (Sadness_weight/n_words)*100,
    Surprise_weight = (Surprise_weight/n_words)*100,
    Trust_weight = (Trust_weight/n_words)*100
  )%>%
  group_by(Year, Thema)%>%
  summarise(
    Anger_mean = mean(Anger_weight),
    Anticipation_mean = mean(Anticipation_weight),
    Disgust_mean = mean(Disgust_weight),
    Fear_mean = mean(Fear_weight),
    Joy_mean = mean(Joy_weight),
    Sadness_mean = mean(Sadness_weight),
    Surprise_mean = mean(Surprise_weight),
    Trust_mean = mean(Trust_weight)
  )

# reshape data frame: columns to rows
# -----------------------------------
Y_aggr_long <- gather(Y_aggr, key = Emotion, value = Value, 2:9)
Y_aggr_categ_long <- gather(Y_aggr_categ, key = Emotion, value = Value, 3:10)
Y_aggr_lda_long <- gather(Y_aggr_lda, key = Emotion, value = Value, 3:10)

```

## Liste der Top-Emotionen-Wörter


Mit Hilfe der Liste mit der Anzahl der Emotionswörtern sowie den jeweiligen Emotionswerten können die für die Analyseergebnisse ausschlaggebendsten Wörter für jede Emotion identifiziert werden. Dafür wurde die Anzahl der Wörter aus der FAZ mit dem Emotionswert multipliziert. Durch das Ordnen nach diesem Produkt können die Wörter gefunden werden, die die Ergebnisse am stärksten bestimmt haben. Zum Beispiel hat das Wort "streit" den größten Einfluss für die Emotion "Wut".

```{r}

# ==============================================================================
# 3) List with top words per emotion
# ==============================================================================

# top word per emotion 
# -------------------
top_10 <- emotions_count_full %>%                                     
  arrange(desc(importance)) %>% 
  group_by(Emotion) %>%
  slice(1:10)

# display as latex table
# ----------------------
knitr::kable(top_10, "simple")

# how many words could be associated with an emotion score from NRC?
# -------------------------------------------------------------------
emotion_share = sum(emotions_count_full$Count)/sum(Y$n_words)
emotion_share

```

## Plots

```{r}


# ==============================================================================
# 4) Plots
# ==============================================================================

# ==============================================================================
# 4.1) Full sample
# ==============================================================================


# full sample: plot average emotion scores per year
#-------------------------------------------------
plot1 <- ggplot(Y_aggr, aes(x = Year))+
  #geom_line(aes(y = Anger_mean, color = emotions[1]), size = 1)+
  #geom_line(aes(y = Anticipation_mean, color = emotions[2]), size  = 1)+
  #geom_line(aes(y = Disgust_mean, color = emotions[3]), size  = 1)+
  #geom_line(aes(y = Fear_mean, color = emotions[4]), size  = 1)+
  #geom_line(aes(y = Joy_mean, color = emotions[5]), size  = 1)+
  #geom_line(aes(y = Sadness_mean, color = emotions[6]), size  = 1)+
  #geom_line(aes(y = Surprise_mean, color = emotions[7]), size  = 1)+
  #geom_line(aes(y = Trust_mean, color = emotions[8]), size  = 1)+
  geom_smooth(aes(y = Anger_mean, color = emotions[1]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Anticipation_mean, color = emotions[2]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Disgust_mean, color = emotions[3]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Fear_mean, color = emotions[4]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Joy_mean, color = emotions[5]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Sadness_mean, color = emotions[6]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Surprise_mean, color = emotions[7]), size = 1, span = 0.1, se = F)+
  geom_smooth(aes(y = Trust_mean, color = emotions[8]), size = 1, span = 0.1, se = F)+
    scale_colour_manual(name="", breaks = emotions,
                      values = c("red", "blue", "green", "black", "yellow", "light blue", "orange", "purple"))+
    scale_y_continuous(expand = c(0, 0), limits=c(0,1.6),breaks=seq(0,1.5,0.5)) +
  theme_classic()+
  theme(legend.position="bottom"
        ,legend.text = element_text(size=12)
        ,axis.text=element_text(size=12,colour="black"))+
  labs(x = "",y = "Emotionenwert")

plot1


# ==============================================================================
# 4.2) Main topics
# ==============================================================================

# plot by main topics (Kategorien)
# -------------------------------
plot2 <- ggplot(Y_aggr_categ_long, aes(x = Year, y = Value, color = Emotion))+
         #geom_smooth(size = 1, span = 0.1, se = F)+
         geom_line(size = 1)+
  scale_colour_manual(name="",values = c("red", "blue", "green", "black", "yellow", 
                                 "light blue", "orange", "purple"),
                      labels = emotions)+
  facet_wrap(~Kategorie, labeller = labeller(Kategorie =label_wrap_gen(25)))+
  labs(x = "",y = "Emotionenwert")+
    theme_bw() + theme(panel.border = element_blank()
                     ,strip.background = element_blank()
                     ,strip.text = element_text(size=12)
                     ,panel.grid.major = element_blank()
                     ,panel.grid.minor = element_blank()
                     ,axis.line = element_line(colour = "black")
                     ,axis.text=element_text(size=12,colour="black")
                     ,legend.position = "bottom"
                     ,legend.text = element_text(size=12)
                     )

plot2

# ==============================================================================
# 4.3) Sub topics
# ==============================================================================

# plot by sub topics
# -----------------
plot3 <- ggplot(Y_aggr_lda, aes(x = Year))+
  #geom_line(aes(y = Anger_mean, color = emotions[1]))+
  #geom_line(aes(y = Anticipation_mean, color = emotions[2]))+
  #geom_line(aes(y = Disgust_mean, color = emotions[3]))+
  #geom_line(aes(y = Fear_mean, color = emotions[4]))+
  #geom_line(aes(y = Joy_mean, color = emotions[5]))+
  #geom_line(aes(y = Sadness_mean, color = emotions[6]))+
  #geom_line(aes(y = Surprise_mean, color = emotions[7]))+
  #geom_line(aes(y = Trust_mean, color = emotions[8]))+
    geom_smooth(aes(y = Anger_mean, color = emotions[1]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Anticipation_mean, color = emotions[2]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Disgust_mean, color = emotions[3]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Fear_mean, color = emotions[4]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Joy_mean, color = emotions[5]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Sadness_mean, color = emotions[6]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Surprise_mean, color = emotions[7]), size = 1, span = 0.2, se = F)+
    geom_smooth(aes(y = Trust_mean, color = emotions[8]), size = 1, span = 0.2, se = F)+
    scale_colour_manual(name="", breaks = emotions,
                      values = c("red", "blue", "green", "black", "yellow", "light blue", "orange", "purple"))+
  facet_wrap(vars(Thema), labeller=label_wrap_gen(width = 25, multi_line = TRUE))+
  labs(x = "",y = "Emotionenwert")+
  scale_y_continuous(expand = c(0, 0), limits=c(0,1.5),breaks=seq(0,1.5,1)) +
    theme_bw() + theme(panel.border = element_blank()
                     ,strip.background = element_blank()
                     ,strip.text = element_text(size=12)
                     ,panel.grid.major = element_blank()
                     ,panel.grid.minor = element_blank()
                     ,axis.line = element_line(colour = "black")
                     ,axis.text=element_text(size=12,colour="black")
                     ,legend.position = "bottom"
                     ,legend.text = element_text(size=12)
                     )


plot3


# ==============================================================================
# 5) Clean and save
# ==============================================================================

# save plots as pdf
# ---------------
plot_out <- list(plot1, plot2, plot3)


pdf(paste0(sFolder1, sOutFile),width=7, height=5)
plot_out
dev.off()

# ==============================================================================
# End of file
# ==============================================================================
```

